---
title: "Understanding Ohm's Law"
subtitle: "Answer Key"
author: "Tristan Caro"
date: "Last knitted `r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: inline
---

# Questions
> 1. How would you expect voltage to change if we kept resistance constant but increased current?

Voltage would increase. According to $V = IR$, voltage is proportional to current and resistance. Therefore, as current increases, the electric pressure (Voltage) on the system will also.

> 2. You want to choose a resistor that can supply 4 volts at 20 mA (milliampere) What strength of resistance should you choose?

We can solve using $R = \frac{V}{I}$ where $V = 4V$ and $I = 0.02A$
```{r}
R = 4*0.02
R
```
We would want a $0.08\Omega$ or $8m\Omega$ resistor.

> 3. Try plotting the same plot we did before, but using a power supply that provides voltage of 3 volts. What do you notice?

The current is lower for all values of resistance.

```{r}
library(tidyverse)
t1 <- tibble(
  voltage = c(9,9,9,9,9,9,3,3,3,3,3,3),
  resistance = c(1,2,5,10,20,50,1,2,5,10,20,50),
  HL = c("H","H","H","H","H","H","L","L","L","L","L","L")
)

t1 <- t1 %>%
  mutate(amperage = voltage / resistance)

plot2 <- ggplot(data = t1, aes(x = resistance, y = amperage, color = HL)) +
  geom_line()
plot2

```


> 4. Resistance, as defined here, only relates to direct current (DC) systems. Doing some googling, what term defines the "resistance" of alternating current (AC) systems?

"Resistance" of AC systems is given by impedance, which is similar to resistance but includes a phase term. This is because alternating currents are defined using wave functions which have amplitude, frequency, phase, etc.