---
title: "Understanding Ohm's Law"
subtitle: "Using R Tibbles"
author: "Tristan Caro"
date: "Last knitted `r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: inline
---

# Learning Goals
- Describe the importance of Ohm's law
- Input values and `mutate()` them using tibbles
- Plot tibble data using `ggplot()`

# Introduction
Ohm's law is fundamental to understanding the basics of how electricity behaves. The law describes the relationship between voltage, amperage, and resistance.
- Voltage: The difference in electric potential. Can be thought about as the "pressure" between two points. Metaphorically alike to water pushing up against a dam, electricity exerts a pressure on the systems it moves through. This is measured in *volts*.
- Current: The rate of flow of electric charge. This is measured in *amperes*.
- Resistance: A value inherent to an object that measures how much it opposes the flow of electric current. This is measured in *ohms*.

These are related by Ohm's law as such:
$$
V = IR
$$
Depending on what value you are trying to determine, the equation can be rearranged accordingly to...
$$
I = \frac{V}{R} \\
or \\
R = \frac{V}{I}
$$
Where V = voltage, I = current, R = resistance.
# Example
We can start by loading our favorite library, the tidyverse.
```{r}
library(tidyverse)
```

Let's say we have a power supply pushing a constant voltage (9V) through a wire. We have a box full of resistors we are going to add to the wire and we are curious how the amperage will change. Let's define a tibble to include various resistor values and a constant voltage. We will let amperage = `NA` so that we can fill it in later.

```{r}
t1 <- tibble(
  voltage = 9,
  resistance = c(1,2,5,10,20,50)
)
t1
```

Now we need to use the `mutate` function to create a new column with our amperages, calculated using Ohm's law. Here we use

$$
I = \frac{V}{R}
$$

```{r}
t1 <- t1 %>%
  mutate(amperage = voltage / resistance)
t1
```

Great! Now we can plot the change in amperage as a function of resistance using `ggplot`.

```{r}
plot1 <- ggplot(data = t1, aes(x = resistance, y = amperage)) +
  geom_line(color = "red")
plot1
```

What do you notice about this trend? Amperage decreases as we add more resistance to the wire!

# Questions
1. How would you expect voltage to change if we kept resistance constant but increased current?
2. You want to choose a resistor that can supply 4 volts at 20 mA (milliampere) What strength of resistance should you choose?
3. Try plotting the same plot we did before, but using a power supply that provides voltage of 3 volts. What do you notice?
4. Resistance, as defined here, only relates to direct current (DC) systems. Doing some googling, what term defines the "resistance" of alternating current (AC) systems?

